\subsection{Visits, Conferences and Seminars}
\label{sec:Visits}

\subsubsection{Year 2016}
\label{sec:2016}

\begin{itemize}

\item On February 26 2016, Erwin Six was invited to present NOKIA's vision on Software Defined Networks and Network Function Virtualization. 

\item On March 21-24 2016, Moussa Amrani attended the training school on Multi-Paradigm Modelling for Cyber-Physical Systems in Tallinn, Estonia.

\item In April 2016, Gilles Perrouin participated to the International Conference on Software Testing, Verification and Validation, (ICST) 2016, Chicago, IL, USA, where he co-organised a workshop on Model-based testing \cite{Papadakis16}.

\item On April 15-16 2016, Moussa Amrani participated a work-group meeting on Multi-Paradigm Modelling for Cyber-Physical Systems in Vienna, Austria.

\item On April 21 2016, Sagacify were invited to present their AI and NLP software at UNamur. Patrick Heymans attended the presentation. 

\item On May 16-17 2016, Patrick Heymans visited VARIAN and Stanford in Palo Alto and held a workshop to identify variability management challenges.

\item On May 18-20 2016, Patrick Heymans participated to the International Conference on Software Engineering (ICSE), 2016, Austin, TX, USA, where he also attended the Steering Committee Meeting of ESEC-FSE. 

\item In May 2016, Gilles Perrouin and Xavier Devroey participated to the International Conference on Software Engineering (ICSE), 2016, Austin, TX, USA. Gilles presented an invited paper at the VACE workshop \cite{Perrouin16a} and a regular paper at the MISE workshop \cite{Perrouin16}. Xavier gave the talk on featured mutation analysis \cite{Devorey16a}.

\item On May 26-27 2016, Patrick Heymans participated to the Programme Committee meeting of the International Requirements Engineering Conference (RE'16) in Barcelona.

\item In June 2016, Tony Leclercq presented his work entitled ``Beyond De-Facto Standards for Designing Human-Computer Interactions in Configurators" at the Workshop on Engineering Computer-Human Interaction in Recommender Systems in Brussels \cite{Lecelercq16a}.  

\item On August 11-12 2016, Patrick Heymans held a follow-up workshop with VARIAN in Palo Alto on identifying variability management challenges.

\item On September 12-16 2016, Patrick Heymans attended the International Requirements Engineering Conference (RE'16) in Beijing where he gave an invited talk on Formal Semantics of Feature Diagrams upon receiving the retrospective Most Influential Paper award. 

\item On September 27 2016, Laurent Schumacher and Patrick Heymans visited Telenet in Mechelen to hold a workshop on variability management challenges.

\item On November 23 2016, Tony Leclercq attended the Software-Defined Networks days in Paris where he presented a poster presenting  joint work with UCL: ``Configurators: many possibilities for Software Defined Networks" \cite{Leclercq16}.

\item In November 2016, Gilles Perrouin was invited to the ``Serval winter Seminar" (Sedan, France) of the Serval Team (University of Luxembourg, SnT)  where he gave the following presentation: ``Software Engineering for Variability-Intensive Systems."

\item In November 2016, Nicolas Genon particiapted to the Conceptual Modelling conference (ER 2016) in Gifu, Japan, where he gave the presentation ``Unlocking visual understanding: Towards effective keys for diagrams'' \cite{Genon16}.

\item On November 24-25 2016, Moussa Amrani participated a workshop on Multi-Paradigm Modelling for Cyber-Physical Systems in Malaga, Spain.

\item On December 9 2016, Patrick Heymans participated to the habilitation jury (HDR) of Tewfik Ziadi at UPMC in Paris. The topics were variability management and automation. 
\end{itemize}

\subsubsection{Year 2017}
\label{sec:2017}

\begin{itemize}
	\item On February 1-–3 2017, Gilles Perrouin and Xavier Devroey participated 
   to the Eleventh International Workshop on Variability Modelling of 
Software-intensive Systems (Eindhoven, Netherlands), where they coached two 
master students of the university of Namur presenting work on the Jhipster case 
study \cite{Halin17}.
    
   \item In February 2017, Moussa Amrani participated to the Modelswards 
Conference in Porto, Portugal and presented his work on the definition of a 
Domain-Specific Language to capture various aspects of Internet of Things 
infrastructures \cite{Amrani-Gilson-Debieche-Englebert:2017}.
    
	\item On March 13--17 2017, Gilles Perrouin and Xavier Devroey participated 
to the International Conference on Software Testing, Verification and 
Validation (Tokyo, Japan), where Xavier Devroey presented the paper on mutation 
equivalence \cite{DBLP:conf/icst/DevroeyPPLSH17}. They also attended to the 
mutation workshop, where Thomas Loise presented his master internship results 
\cite{DBLP:conf/icst/LoiseDPPH17}.
    
   \item On May 4-5 2017, Patrick Heymans participated to the Programme 
Committee meeting of the International Requirements Engineering Conference 
(RE'17) in Lexington, KY, USA.
    
   \item In May 14-17 2017, Moussa Amrani and James Jerson Ortiz Vega 
attended the Nasa Formal Methods Conference (NFM) held in Moffet Field, CA, 
USA, and presented a paper on efficient model-checking of multi-timed automata 
\cite{Ortiz-Amrani-Schobbens:2017}.
   
   \item In May 2017, Laurent Schumacher participated to the IEEE International 
Conference on Communications (ICC) in Paris.
   
   \item During June 2017, several scholars were invited by our research group 
to exchange on variability-intensive systems:
    \begin{itemize}
    \item Prof. Vander Alves from University of Brasilia,
    \item Dr. Mathieu Acher,
    \item Dr. Axel Legay from INRIA-Rennes,
    \item Prof. Benoît Baudry from KTH (Sweden),
    \item Prof. Myra Cohen from University of Nebraska-Lincoln.
	\end{itemize}
   
   \item On June 21-23 2017, Jean-Marc Davril participated to the 22nd 
International Conference on Natural Language \& Information Systems (NLDB), that 
was held in Li{\`e}ge, and presented his work entitled ``Technical Aspect 
Extraction from Customer Reviews based on Seeded Word Clustering" 
\cite{Davril17}.  
   
   \item On July 3 2017, Patrick Heymans and Laurent Schumacher participated to 
a half-day exchange session at Multitel in Mons.
   
   \item On September 14-15, Patrick Heymans participated to the yearly 
international Configuration Workshop (ConfWS), this time held in Paris.
   
   \item  In September 2017, Gilles Perrouin, Xavier Devroey and Maxime Cordy 
participated to the International Systems and Software Product Line Conference 
(SPLC) in Seville, Spain where they presented their tutorial on testing 
variability-intensive systems \cite{DBLP:conf/splc/PerrouinDC17}. 
   
   \item On October 11 2017, Gilles Perrouin presented research carried out in 
the PReCISE center on variability-intensive systems at the CNRS working group on 
software product lines (LOUISE), in Paris France.
    
   \item On October 31 2017, Patrick Heymans and Gilles Perrouin presented an 
overview of their research on variability-intensive systems during an Industry 
4.0 session during a series of events held at UNamur.
    
   \item On November 16 2017, Patrick Heymans, Laurent Schumacher and Tony 
Leclercq held an online workshop with NextiraOne, a french company pioneering 
Software Defined Networks, to initiate collaboration.
    
   \item On December 14-15 2017, Patrick Heymans and John Pyrgies visited the 
CED (Centre d'Excellence Drone) in Salon de Provence to initiate a doctoral 
thesis and broader collaboration.
\end{itemize}

\subsubsection{Year 2018}
\label{sec:2018}

\begin{itemize}
   \item On June 2018, Moussa Amrani, together with Vincent Englebert and 
Fabian Gilson, published a paper on how to handle complex scenarios in Smart 
Home equipped with IoT devices, described with Complex Event Processing 
technologies \cite{Amrani-Gilson-Englebert:2017}.

   \item On July 16-20, Gilles Perrouin and James Jerson Ortiz Vega attended 
the International Conference on Software Quality, Reliability and Security 
(QRS) held in Porto, Portugal, and presented a survey paper co-authored with 
Moussa Amrani and Pierre-Yves Schobbens on the use of Mutation Testing for 
Real-Time frameworks \cite{OrtizVega-Perrouin-Amrani-Schobbens:2018}.

   \item On October 16, 2018, Moussa Amrani presented a full-day tutorial on 
the integration of Machine Learning for Formal Verification tools at the 
International Conference on Model Driven Engineering Languages and Systems 
(MoDELS) held in Copenhaguen, Denmark.

   \item On November 18--24 2018, Moussa Amrani actively participated in a 
Summer School on Multi-Modelling of Cyber-Physical Systems held in Pisa, Italy, 
demontrated an approach based on the Esterel \textsc{Scade} tool for describing 
the computer decisions, and on \textsc{Ansys} Simplorer for capturing the 
multi-physics behaviour.

   \item On November 24--26 2018, Moussa Amrani participated in the final 
Workshop of the \textsc{Cost} Action on Multi-Modelling Paradigms for 
Cyber-Physical Systems (\textsc{Mpm4Cps}) held in Pisa, Italy.
\end{itemize}



\subsection{Publications}
\label{sec:Publications}

The list of publications for the period covered by the report is given below: 

\nocite{*}
\printbibliography[heading={none}]
